---
title: "Regression Models Course Project"
author: "Zirui Wang"
date: "4/25/2021"
output: html_document
---

### Project description
You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:
1.Is an automatic or manual transmission better for MPG.
2.Quantify the MPG difference between automatic and manual transmissions.

## Exploratory data analyses
```{r}
data('mtcars')
head(mtcars, n=5)
summary(mtcars)
library(caret)
featurePlot(x=mtcars[, c('cyl','disp','hp')], y=mtcars$mpg, plot='pairs')
featurePlot(x=mtcars[, c('drat','wt','qsec')], y=mtcars$mpg, plot='pairs')
featurePlot(x=mtcars[, c('vs','am','gear','carb')], y=mtcars$mpg, plot='pairs')
boxplot(mpg~am, data=mtcars, col=c('yellow', 'green'), main='Transimission vs MPG', xlab = 'Transmission', ylab = 'Mile per Gallon(mpg)')
```

## Hypothesis test with bootstrap
```{r}
mpg_auto <- mtcars$mpg[mtcars$am==1]
mpg_manu <- mtcars$mpg[mtcars$am==0]
resamples_auto <- matrix(sample(mpg_auto, 10*10, replace = TRUE), 10, 10)
resamples_manu <- matrix(sample(mpg_manu, 10*10, replace = TRUE), 10, 10)
means_auto <- apply(resamples_auto, 1, mean)
means_manu <- apply(resamples_manu, 1, mean)
t.test(means_auto-means_manu)
```
The positive 95% confidence interval suggests that automatic vehicles yield higher mile per gallon (MPG) than manual vehicles. 

## Build a linear regression model
```{r}
fit <- lm(mpg ~ ., data=mtcars)
summary(fit)
anova(fit)
par(mfrow = c(2,2), oma=c(0,0,4,0))
plot(fit, main = NULL)
```

## Build a Logistics Regression Model
```{r}
logRegM <- glm(am ~ mpg, data=mtcars, family='binomial')
summary(logRegM)
exp(logRegM$coeff)
exp(confint(logRegM))
```
We expect a 36% probability of increase in cars being automatic for every MPG increase. 

## Plot Logistic Regression Model
```{r}
newd <- seq(10, 40, len=50)
y_pred <- predict(logRegM, newdata=data.frame(mpg=newd), type = 'response')
plot(mtcars$mpg, mtcars$am)
lines(newd, y_pred, col='green', lwd=5)
```

## Conclusion
Based on the linear regression model and logistic regression model, we conclude that automatic transmission is better for MPG than manual transmission. 
