---
title: "Statistical Inference Project Part 1"
author: "Zirui Wang"
date: "4/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Simulation Exercise

This project investigates the exponential distribution in R and compare it with the Central Limit Theorem. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 for all of the simulations.  

**Show the sample mean and compare it to the theoretical mean of the distribution.** 

```{r}
nsim <- 1000
lambda <- 0.2
n <- 40
samplemeans <- NULL
samplevariances <- NULL
for (i in 1:nsim) {
  samplemeans <- c(samplemeans, mean(rexp(n, lambda)))
  samplevariances <- c(samplevariances, var(rexp(n, lambda)))
}
rbind(c('Sample mean', 'Theoretical mean'), c(round(mean(samplemeans),3), 1/lambda))
hist(samplemeans, breaks=n)
```

**Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.**

```{r}
rbind(c('Sample variance','Theoretical variance'),c(round(mean(samplevariances),3),(1/lambda)^2))
hist(samplevariances, breaks=n)
```

**Show that the distribution is approximately normal.**

```{r}
hist(samplemeans, breaks = n, prob = T, xlab = "Means")
x <- seq(min(samplemeans), max(samplemeans), length=n)
lines(x, dnorm(x, mean = 1/lambda, sd = (1/lambda/sqrt(n))))
qqnorm(samplemeans)
qqline(samplemeans)
```