---
title: "Practical Machine Learning"
author: "Zirui Wang"
date: "5/11/2021"
output: html_document
---
---
title: "Practical Machine Learning"
author: "Zirui Wang"
date: "5/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Project description
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

## Loadind, cleaning and preprocessing traning data
```{r}
library(caret)
data <- read.csv(url('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv'))
# move all NA coloumn
cleandata <- data[ , colSums(is.na(data)) == 0]
inTrain <- createDataPartition(y=cleandata$classe, p=0.7, list=FALSE)
training <- cleandata[inTrain,]
testing <- cleandata[-inTrain,]
# remove variables with Nearly Zero Variance
NZV <- nearZeroVar(training)
training <- training[, -NZV]
testing  <- testing[, -NZV]
# remove identification only variables (columns 1 to 5)
training <- training[, -(1:5)]
testing  <- testing[, -(1:5)]
```

## Decision tree model
```{r}
library(rpart)
library(RColorBrewer)
library(rattle)
dt_model <- train(classe~., method='rpart', data=training)
fancyRpartPlot(dt_model$finalModel)
dt_pred <- predict(dt_model, testing)
confusionMatrix(dt_pred, as.factor(testing$classe))$overall[1]
```

## Random forests model
```{r}
controlRF <- trainControl(method="cv", number=3, verboseIter=FALSE) #cross validation
rf_model <- train(classe~., method='rf', data=training, trControl=controlRF, verbose = FALSE)
rf_pred <- predict(rf_model, testing)
confusionMatrix(rf_pred, as.factor(testing$classe))$overall[1]
plot(rf_model$finalModel)
```

## Generalized boosted model
```{r}
controlGBM <- trainControl(method="repeatedcv", number=3, verboseIter=FALSE) #cross validation
gbm_model <- train(classe~., method='gbm', data=training, trControl = controlGBM, verbose = FALSE)
gbm_pred <- predict(gbm_model, testing)
confusionMatrix(gbm_pred, as.factor(testing$classe))$overall[1]
plot(gbm_model)
```

## Plot on RF and GBM
```{r}
qplot(rf_pred, gbm_pred, colour=classe, data=testing)
```

## RF and GBM combined model
```{r}
predDF <- data.frame(rf_pred, gbm_pred, classe=testing$classe)
comb_model <- train(classe~., method='gam', preProcess='pca', data=predDF)
comb_pred <- predict(comb_model, predDF)
confusionMatrix(comb_pred, as.factor(testing$classe))$overall[1]
plot(comb_model)
```

## Prediction Test
```{r}
validation <- read.csv(url('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv'))
cleanvd <- validation[ , colSums(is.na(validation)) == 0]
NZVvd <- nearZeroVar(cleanvd)
cleanvd <- cleanvd[, -NZVvd]
predict(rf_model, cleanvd)
```